Information Aggregation in Exponential Family Markets

### 2014-04-22 WriteUp/maxentpredmkts.tex
added references to Raf's work (from his email)

Prediction markets are known to perform well in practice~\citep{AGT07,pennock2001real}. However, a sound theory for interpreting trader behavior and market prices is an ongoing area of study~\citep{wolfers2006interpreting}. At one extreme, agents are assumed myopic and risk-neutral, implying they move the market state to their belief~\citep{chen2010new}. At the other extreme, agents are strategic and the market fully incorporates all information~\citep{ostrovsky2012}. 
% Strategic behavior in prediction markets is addressed in~\citep{chen2010gaming,dimitrov08}.
The aggregation properties of market mechanisms have also been explored from a machine learning perspective in~\cite{storkey11}.

We are not aware of any works that consider risk-averse agents within cost-function based markets. However, risk aversion is a fundamental component of mathematical finance and portfolio optimization, and there are close connections between the notion of a cost function and that of a convex risk measure~\citep{follmerRisk,follmer2011entropic}. Indeed, they arise from the same axioms as noted by~\citet{othman2011liqu}. We see the potential to draw more on the mathematical finance literature to take into account risk aversion, as prediction markets are simply single-period financial markets~\citep[Part I]{follmerFinance}.

>>>>

Prediction markets are known to perform well in practice~\citep{AGT07,pennock2001real}. However, a sound theory for interpreting trader behavior and market prices is an ongoing area of study~\citep{wolfers2006interpreting}. At one extreme, agents are assumed myopic and risk-neutral, implying they move the market state to their belief~\citep{chen2010new}. At the other extreme, agents are strategic and the market fully incorporates all information~\citep{ostrovsky2012}. 
% Strategic behavior in prediction markets is addressed in~\citep{chen2010gaming,dimitrov08}.
The aggregation properties of market mechanisms have also been explored from a machine learning perspective in~\cite{storkey11}. More closely related to our work, \citet{FrongilloRe13} also touch upon the statistical interpretations of prediction market costs and payoffs from the viewpoint of exponential families.

We are not aware of any works that consider risk-averse agents within cost-function based markets, with the exception of~\citep[Sec.\ 3.1]{FrongilloPeRe12} who assume agents are price takers. However, risk aversion is a fundamental component of mathematical finance and portfolio optimization, and there are close connections between the notion of a cost function and that of a convex risk measure~\citep{follmerRisk,follmer2011entropic}. Indeed, they arise from the same axioms as noted by~\citet{othman2011liqu}. We see the potential to draw more on the mathematical finance literature to take into account risk aversion, as prediction markets are simply single-period financial markets~\citep[Part I]{follmerFinance}.
